% !TeX spellcheck = en_US
\documentclass[11pt, a4paper, oneside]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{psfrag}
\usepackage[dvi-ps]{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

%\usepackage{bbold}
\usepackage{amssymb}
\usepackage{amsmath}
\def\??{\hbox{{1}\kern-.25em\hbox{l}}}
\usepackage{float}
\usepackage{todonotes}
\pagestyle{empty}
\usepackage{stackengine} 

\date{}



\begin{document}
	
Testing of the \texttt{SpinGlassPEPS.jl}, PEPS and MPS-MPO implementation of 
the finding the ground state of the spins system. spins were structured in the 
following form:
\begin{itemize}
	\item grid - PEPS (one spin node exact and approximation and multi spin 
	nodes), mpo-mps (one spin nodes);
	\item arbitrary graph - mpo-mps.
	\item chimera graph - PEPS.
\end{itemize}
Testing were preformed both on random instances, `droplet' instances supplied 
from the Spin-Glass solver 
\texttt{https://github.com/marekrams/tnac4o}
and the small instance of the logistic problem of railway 
dispatching. In the case of the random instances, output was compared with the 
brute force computation. 

Particular testing:
\begin{itemize}
	\item \texttt{tests\_on\_data.jl} -- PEPS on grid (random), MPO-MPS on 
	logistic instance (arbitrary graph),
	\item \texttt{tests\_of\_solvers.jl} -- larger spectrum MPO-MPS full graph 
	up to $L = 64$, PEPS grid.
	\item \texttt{tests\_grid\_from\_file.jl} -- grid of size $5x5$ or $6x6$ 
	data given in file, compaer with brute force output,
	\item \texttt{tests\_on\_chimera.jl} -- PEPS on chimera for now done up to 
	$512$ -- energies eqqual or lower (better solutions) than in droplet. 
	Various $\chi$ - various computational time.
\end{itemize}



\end{document}





